---
title: "Research paper_First draft"
author: "Ngan Nguyen"
date: "2025-11-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(ggplot2)
library(readxl)
library(tidyr)
library(tidyverse)
library(purrr)
library(stringr)
library(scales)
library(patchwork)
library(fixest)
library(broom)
library(tibble)
library(sandwich)
library(lmtest)



```

# I/ Data Cleaning
```{r, message = FALSE}

total_intstudents_us <- read.csv("total_intstudents_us.csv")

```

## 1/ Total students studying in the United States from 2014 to 2023
```{r}
# Remove columns & row with only empty
total_intstudents_us_new <- total_intstudents_us %>%
  select(where(~ any(!is.na(.)))) %>%
  filter(rowSums(is.na(.)) < ncol(.))
# Rename the first cell in first column to "Academic_year"
total_intstudents_us_new[1,1] <- "Academic_year"
total_intstudents_us_new[2,1] <- "Academic_level"
colnames(total_intstudents_us_new)[1] <- "Country"
# Drop any columns that have "OPT" or "Other" or "Non-Degree"
total_intstudents_us_new <- total_intstudents_us_new[, !(total_intstudents_us_new[2, ] %in% c("Other", "OPT", "Non-Degree"))]
# Loop through the columns (2nd, 5th, etc.) and update them
for (j in seq(2, ncol(total_intstudents_us_new), by = 2)) {
  value <- total_intstudents_us_new[1, j]  # Get the value from the current column (e.g., Year_1, Year_4)
  
# Assign the value to the next two columns (spread across Year_2, Year_3, Year_5, Year_6)
  if (j + 1 <= ncol(total_intstudents_us_new)) total_intstudents_us_new[1, j + 1] <- value}


```



```{r}
# Convert the data set
# Take first two column for transpose
header_rows <- total_intstudents_us_new[1:2, ]
header_tidy <- as.data.frame(t(header_rows), stringsAsFactors = FALSE)
names(header_tidy) <- c("Academic_year", "Academic_level")
header_tidy <- header_tidy[-1, ] |> as_tibble()

# Step 2: Extract academic years and levels from the first two rows
academic_years <- as.character(total_intstudents_us_new[1, ])
academic_levels <- as.character(total_intstudents_us_new[2, ])

# Step 3: Create combined column names
col_names <- paste0(academic_years, "_", academic_levels)

# Step 4: Assign proper column names
names(total_intstudents_us_new) <- col_names

# Step 5: Remove the first two rows (since they are headers)
data_clean <- total_intstudents_us_new[-c(1, 2), ]

# Step 6: Rename the first column as "Country"
names(data_clean)[1] <- "Country"

# Step 7: Convert from wide to long format
data_long <- data_clean %>%
  pivot_longer(
    cols = -Country,
    names_to = "Year_Level",
    values_to = "total_students_each_year"
  )

# Step 8: Split combined column into Academic_year and Academic_level
data_long <- data_long %>%
  separate(Year_Level, into = c("Academic_year", "Academic_level"), sep = "_")

# Step 9: (Optional) Join with header_tidy to ensure matching year/level pairs
final_data <- data_long %>%
  inner_join(header_tidy, by = c("Academic_year", "Academic_level"))

# Step 10: Reorder columns
final_data <- final_data %>%
  select(Country, Academic_year, Academic_level, total_students_each_year)
# Step 11: make sure to add the study destination "united_states" for this data set
final_data <- final_data %>%
  mutate(study_destination = "United States")
# Filter only have asian countries
asian_countries <- c(
  "China", "India", "Kazakhstan", "Vietnam", "Afghanistan", "Bangladesh", "Bhutan", "Brunei", "Cambodia", "Indonesia", "Laos", "Malaysia", "Maldives", "Burma/Myanmar", "Nepal", "Pakistan", "Philippines", "Singapore", "Sri Lanka", "Thailand", "Timor-Leste", "South Korea", "North Korea", "Hong Kong", "Japan", "Mongolia", "Kyrgyzstan", "Tajikistan", "Turkmenistan", "Uzbekistan", "Macau"
)

# Assuming your final combined dataset is called combined_data
final_data <- final_data %>%
  filter(Country %in% asian_countries)
# Convert the column "total_students_each_year" to be value
final_data$total_students_each_year <- as.integer(final_data$total_students_each_year)

# Group by Academic_year and Country, then sum total_students_each_year
final_data_us_by_aclevel <- final_data %>%
  group_by(Academic_year, Country,study_destination) %>%
  summarise(total_students = sum(total_students_each_year, na.rm = TRUE))

# Convert to the ending year (e.g. "2001", "2002", etc.)
final_data_us_by_aclevel$Academic_year <- as.numeric(sub(".*/", "20", final_data_us_by_aclevel$Academic_year))
# Add destination column (United States)for merging later
final_data_us_by_aclevel <- final_data_us_by_aclevel %>%
  mutate(destination = "United States")

```




## 2/ Total students studying in Europe Country from 2014 to 2023


```{r, message = FALSE, warning=FALSE}
# Define folder
folder_path <- "~/Downloads/studydestination_europe"

# List all CSV files (use full paths so R reads from the correct folder)
files <- list.files(path = folder_path, pattern = "\\.csv$", full.names = TRUE)

# Function to clean each dataset
clean_europe_data1 <- function(file) {
  # Read the main data (skip metadata)
  europe_data1 <- read.csv(file, skip = 9)
  
  # Keep only the first 43 rows
  europe_data1 <- europe_data1[1:43, , drop = FALSE]
  
  # Remove odd-numbered columns starting from the 3rd
  cols_to_remove1 <- seq(3, ncol(europe_data1), by = 2)
  europe_data1 <- europe_data1[, -cols_to_remove1, drop = FALSE]
  
  # Read the raw file (no skip) to extract country and academic level
  raw_data1 <- read.csv(file, header = FALSE)
  
  # Extract metadata
  country_name1 <- as.character(raw_data1[7, 3])
  academic_level1 <- as.character(raw_data1[9, 3])
  
  # Safety check in case file has fewer than 11 columns
  max_col <- min(11, ncol(europe_data1))
  if (ncol(europe_data1) >= 2) {
    new_colnames1 <- as.character(unlist(europe_data1[1, 2:max_col]))
    names(europe_data1)[2:max_col] <- new_colnames1
  }
  
  # Remove that first row (used for column names) and GEO labels and total of European Union
  europe_data1 <- europe_data1[-c(1:4), , drop = FALSE]
  
  # --- Rename first column to "Country" ---
 cols_to_convert <- 2:min(11, ncol(europe_data1))
  europe_data1[, cols_to_convert] <- lapply(
    europe_data1[, cols_to_convert],
    function(x) {
      # Remove commas, trim spaces
      x_clean <- gsub(",", "", x)
      x_clean <- trimws(x_clean)
      # Convert to numeric
      x_num <- as.numeric(x_clean)
      # Replace NA with 0
      x_num[is.na(x_num)] <- 0
      return(x_num)
    }
  )
  # Add new columns
  europe_data1$country <- country_name1
  europe_data1$academic_level <- academic_level1
  europe_data1$source_file <- basename(file)

  return(europe_data1)
}
# Exclude certains countries withh missing value more than half of periods (2014 to 2023)
remove_list <- c(
  "Bosnia and Herzegovina",
  "Montenegro",
  "Georgia",
  "Albania",
  "United Kingdom",
  "Netherlands"
)
# Apply cleaning and remove unwanted countries
all_europe_data1 <- lapply(
  files,
  function(f) {
    df <- clean_europe_data1(f)
    df[!(df$X %in% remove_list), ]
  }
)

```





* Sum up by year, academic level, X (country of destination) and country of origin

```{r, message=FALSE}
# Sum up by year, academic level, X (country of destination) and country
all_summarized1 <- lapply(
  all_europe_data1,
  function(df) {
    df %>%
      rename(destination = X) %>%   
      pivot_longer(
        cols = 2:11,
        names_to = "Academic_year",
        values_to = "total_students"
      ) %>%
      group_by(Academic_year, country, destination) %>%   # <-- use new name
      summarise(total_students_each_year = sum(total_students, na.rm = TRUE)) %>%
      ungroup()
  }
)
```

```{r}

```


* Sum up by year, academic level, and country of origin

```{r message = FALSE}
# Sum up by year and academic level, country
all_summarized <- lapply(all_europe_data1,function(df) {
  df %>%
    pivot_longer(
      cols = 2:11,
      names_to = "Academic_year",
      values_to = "total_students"
    ) %>%
    group_by(Academic_year, country) %>%
    summarise(total_students_each_year = sum(total_students, na.rm = TRUE)) %>%
    ungroup()
})
```




```{r}
# Put all data in one place (one dataset) together
final_data_europe_by_aclevel <- bind_rows(all_summarized1)
final_data_europe_by_aclevel <- final_data_europe_by_aclevel %>%
  mutate(study_destination = "Europe")

```

```{r}
final_data_europe_by_aclevel
```



```{r}
names(final_data_europe_by_aclevel)[2] <- "Country"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Macao"] <- "Macau"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Brunei Darussalam"] <- "Brunei"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Viet Nam"] <- "Vietnam"

# Group by one more time 
final_data_europe_by_aclevel1 <- final_data_europe_by_aclevel %>%
  filter(Country %in% asian_countries) %>%
  group_by(Academic_year, Country, study_destination, destination) %>%
   summarise(total_students= sum(total_students_each_year, na.rm = TRUE))
             
final_data_europe_by_aclevel1$Academic_year <- as.numeric(final_data_europe_by_aclevel1$Academic_year)

combined_data <- bind_rows(final_data_europe_by_aclevel1, final_data_us_by_aclevel) %>%
  filter(Academic_year >= 2016& Academic_year <= 2023)
```




## 3/ Economic/Social indicators 

### GDP (current $USD)
```{r}
gdp <- read.csv("GDP.csv", header = FALSE)
# Remove the first 2 rows
gdp1 <- gdp[-c(1,2), , drop = FALSE]

# Use the first row as column names
colnames(gdp1) <- as.character(unlist(gdp1[1, ]))

# Remove the first row from the data
gdp1 <- gdp1[-1, ]
# Rename first column to Country
colnames(gdp1)[1] <- "Country"
# Remove the last missing column
missing_col_index <- which(colnames(gdp1) == "" | is.na(colnames(gdp1)))
missing_col_index
gdp1 <- gdp1[, -missing_col_index]
# Fix the countries naming for merging later
gdp1$Country[gdp1$Country == "Macao"] <- "Macau"
gdp1$Country[gdp1$Country == "Brunei Darussalam"] <- "Brunei"
gdp1$Country[gdp1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
gdp1$Country[gdp1$Country == "Korea, Rep."] <- "South Korea"
gdp1$Country[gdp1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
gdp1$Country[gdp1$Country == "Viet Nam"] <- "Vietnam"
gdp1$Country[gdp1$Country == "Lao PDR"] <- "Laos"
gdp1$Country[gdp1$Country == "Myanmar"] <- "Burma/Myanmar"
gdp1$Country[gdp1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
gdp1$Country[gdp1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
gdp1$Country[gdp1$Country == "Macao SAR, China"] <- "Macau"

# Filter gdp1 based on those countries
gdp1_filtered <- gdp1 %>% filter(Country %in% asian_countries)

```




```{r}
# Change the year naming (ex: 2022/23 to 2023) and convert to numerical
numeric_data <- gdp1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

# Step 2: Pivot all year columns into long format
long_data <- numeric_data %>%
  pivot_longer(
    cols = -Country,          # pivot all except Country
    names_to = "Academic_year",        # the column names become the 'year' variable
    values_to = "gdp"         # the values become 'gdp'
  )

# Step 3: Sum GDP by country and year
yearly_sum_df <- long_data %>%
  group_by(Country, Academic_year) %>%
  summarise(gdp = sum(gdp, na.rm = TRUE), .groups = "drop")
yearly_sum_df$Academic_year <- as.numeric(yearly_sum_df$Academic_year)
```

### net_immigration
```{r}
net_immigration <- read.csv("net_immigration.csv", header = FALSE)
# Remove the first 4 rows
net_immigration1 <- net_immigration[-c(1:4), , drop = FALSE]

# Use the first row as column names
colnames(net_immigration1) <- as.character(unlist(net_immigration1[1, ]))

# Remove the first row from the data
net_immigration1 <- net_immigration1[-1, ]
# Rename first column to Country
colnames(net_immigration1)[1] <- "Country"
# Filter gdp1 based on those countries

net_immigration1$Country[net_immigration1$Country == "Macao"] <- "Macau"
net_immigration1$Country[net_immigration1$Country == "Brunei Darussalam"] <- "Brunei"
net_immigration1$Country[net_immigration1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
net_immigration1$Country[net_immigration1$Country == "Korea, Rep."] <- "South Korea"
net_immigration1$Country[net_immigration1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
net_immigration1$Country[net_immigration1$Country == "Viet Nam"] <- "Vietnam"
net_immigration1$Country[net_immigration1$Country == "Lao PDR"] <- "Laos"
net_immigration1$Country[net_immigration1$Country == "Myanmar"] <- "Burma/Myanmar"
net_immigration1$Country[net_immigration1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
net_immigration1$Country[net_immigration1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
net_immigration1$Country[net_immigration1$Country == "Macao SAR, China"] <- "Macau"

net_immigration1_filtered <- net_immigration1 %>% filter(Country %in% asian_countries)
# 
numeric_data1<- net_immigration1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

long_data1 <- pivot_longer(numeric_data1, 
                          cols = -Country,
                          names_to = "Academic_year",     # Convert column names (the years) into a "year" column
                          values_to = "value")   # Corresponding values go into a "value" column

# Step 3: Sum the values for each year
yearly_sum_net_df <- long_data1 %>%
  group_by(Country, Academic_year) %>%
  summarise(total_value = sum(value, na.rm = TRUE))

yearly_sum_net_df <- yearly_sum_net_df %>%
  rename(net_immigration = total_value)  %>% filter(Country %in% asian_countries)


yearly_sum_net_df$Academic_year <- as.numeric(yearly_sum_net_df$Academic_year)

# Step 4: Print the resulting data
print(yearly_sum_net_df)
```



### unemployment rate

```{r}
unemployment_rate <- read.csv("unemployment_rate.csv", header = FALSE)

```



```{r}
# Remove the first 2 rows
unemployment_rate1 <- unemployment_rate[-c(1,2), , drop = FALSE]

# Use the first row as column names
colnames(unemployment_rate1) <- as.character(unlist(unemployment_rate1[1, ]))

# Remove the first row from the data
unemployment_rate1 <- unemployment_rate1[-1, ]
```





```{r}
colnames(unemployment_rate1)[1] <- "Country"
# Re,move the last missing column
missing_col_index2 <- which(colnames(unemployment_rate1) == "" | is.na(colnames(unemployment_rate1)))
unemployment_rate1 <- unemployment_rate1[, -missing_col_index2]


unemployment_rate1$Country[unemployment_rate1$Country == "Macao"] <- "Macau"
unemployment_rate1$Country[unemployment_rate1$Country == "Brunei Darussalam"] <- "Brunei"
unemployment_rate1$Country[unemployment_rate1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
unemployment_rate1$Country[unemployment_rate1$Country == "Korea, Rep."] <- "South Korea"
unemployment_rate1$Country[unemployment_rate1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
unemployment_rate1$Country[unemployment_rate1$Country == "Viet Nam"] <- "Vietnam"
unemployment_rate1$Country[unemployment_rate1$Country == "Lao PDR"] <- "Laos"
unemployment_rate1$Country[unemployment_rate1$Country == "Myanmar"] <- "Burma/Myanmar"
unemployment_rate1$Country[unemployment_rate1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
unemployment_rate1$Country[unemployment_rate1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
unemployment_rate1$Country[unemployment_rate1$Country == "Macao SAR, China"] <- "Macau"


# Filter gdp1 based on those countries
unemployment_rate1_filtered <- unemployment_rate1 %>% filter(Country %in% asian_countries)
# View the filtered data
head(unemployment_rate1_filtered)
```

```{r}
# Change the year naming (ex: 2022/23 to 2023) and convert to numerical
numeric_data2<- unemployment_rate1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

long_data2 <- pivot_longer(numeric_data2, 
                          cols = -Country,
                          names_to = "Academic_year",     # Convert column names (the years) into a "year" column
                          values_to = "value")   # Corresponding values go into a "value" column

# Step 3: (Optional) Sum the values for each year
yearly_sum_unemployment_df <- long_data2 %>%
  group_by(Country, Academic_year) %>%
  summarise(total_value = sum(value, na.rm = TRUE))

yearly_sum_unemployment_df <- yearly_sum_unemployment_df %>%
  rename(unemployment_rate = total_value)  %>% filter(Country %in% asian_countries)

yearly_sum_unemployment_df$Academic_year <- as.numeric(yearly_sum_unemployment_df$Academic_year)

```




### Population

```{r}
population <- read.csv("population.csv", header = FALSE)

```


```{r}
# Remove the first 2 rows
population1 <- population[-c(1,2), , drop = FALSE]

# Use the first row as column names
colnames(population1) <- as.character(unlist(population1[1, ]))

# Remove the first row from the data
population1 <- population1[-1, ]

```


```{r}
colnames(population1)[1] <- "Country"
# Remove the last missing column
missing_col_index2 <- which(colnames(population1) == "" | is.na(colnames(population1)))
missing_col_index2
population1 <- population1[, -missing_col_index2]


population1$Country[population1$Country == "Macao"] <- "Macau"
population1$Country[population1$Country == "Brunei Darussalam"] <- "Brunei"
population1$Country[population1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
population1$Country[population1$Country == "Korea, Rep."] <- "South Korea"
population1$Country[population1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
population1$Country[population1$Country == "Viet Nam"] <- "Vietnam"
population1$Country[population1$Country == "Lao PDR"] <- "Laos"
population1$Country[population1$Country == "Myanmar"] <- "Burma/Myanmar"
population1$Country[population1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
population1$Country[population1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
population1$Country[population1$Country == "Macao SAR, China"] <- "Macau"




# Filter gdp1 based on those countries
population1_filtered <- population1 %>% filter(Country %in% asian_countries)
# View the filtered data
head(population1_filtered)
```
```{r}
# Change the year naming (ex: 2022/23 to 2023) and convert to numerical
numeric_data3<- population1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

long_data3 <- pivot_longer(numeric_data3, 
                          cols = -Country,
                          names_to = "Academic_year",     # Convert column names (the years) into a "year" column
                          values_to = "value")   # Corresponding values go into a "value" column

# Step 3: (Optional) Sum the values for each year
yearly_sum_population_df <- long_data3 %>%
  group_by(Country, Academic_year) %>%
  summarise(total_value = sum(value, na.rm = TRUE))

yearly_sum_population_df <- yearly_sum_population_df %>%
  rename(population = total_value)  %>% filter(Country %in% asian_countries)

yearly_sum_population_df$Academic_year <- as.numeric(yearly_sum_population_df$Academic_year)
```


### 0DA scholarship data (UNESCO)

```{r}
scholarship <- read.csv("scholarship.csv", header = FALSE)

```

```{r}
# Include full name of country of origin in the data set by 3-letters ( using data of World Bank) 

scholarship1<- scholarship %>%
  left_join(
    population %>% 
      select(Country = 1, match_value = 2),
    by = c("V2" = "match_value")   # V2 = column 2 in scholarship
  )

# Change the countries name for consistency 
scholarship1$Country[scholarship1$Country == "Lao PDR"] <- "Laos"
scholarship1$Country[scholarship1$Country == "Brunei Darussalam"] <- "Brunei"
scholarship1$Country[scholarship1$Country == "Viet Nam"] <- "Vietnam"
scholarship1$Country[scholarship1$Country == "Myanmar"] <- "Burma/Myanmar"
scholarship1$Country[scholarship1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
scholarship1$Country[scholarship1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
scholarship1$Country[scholarship1$Country == "Macao SAR, China"] <- "Macau"
scholarship1$Country[scholarship1$Country == "Korea, Rep."] <- "South Korea"
scholarship1$Country[scholarship1$Country == "Korea, Dem. People's Rep."] <- "North Korea"



scholarship_ODA<- scholarship1%>%
  rename(
    Academic_year = 3,                  # Rename column 3 and 4
    scholarship_ODA_volume = 4
  ) %>%
  select(-1, -2, -5, -6) %>%   # Remove columns 1, 2, 5, 6
  slice(-1)     # Remove the unecessary first row
# Only include countries of Asian students in this paper
scholarship_ODA<- scholarship_ODA%>%
  filter(Country %in% asian_countries)
# Convert year & scholarship volume data to numeric type
scholarship_ODA$Academic_year <- as.numeric(scholarship_ODA$Academic_year)
scholarship_ODA$scholarship_ODA_volume <- as.numeric(scholarship_ODA$scholarship_ODA_volume)

```




```{r}
# List of countries does not eligible for ODA scholarship -> scholarship data will appear as 0 later after joining
setdiff(asian_countries, scholarship_ODA$Country)

```



## Joining economic/social indicators into mobility data

#### * Perform a left join to add gdp, net_immigratiop, scholarship_ODA, total_unemployment_rate to combined_data based on 'year' and 'Academic_year'

```{r}
# Perform a left join to add gdp, net_immigration, population and  to combined_data based on 'year' and 'Academic_year'
combined_data_with_total_value <- combined_data %>%
  left_join(yearly_sum_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_net_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_unemployment_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_population_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(scholarship_ODA, by = c("Academic_year" = "Academic_year", "Country" = "Country"))

```


```{r}
# Replace missing value in scholarship become 0 
combined_data_with_total_value$scholarship_ODA_volume[is.na(combined_data_with_total_value$scholarship_ODA_volume)] <- 0

```
```{r}
# Create log(population)
combined_data_with_total_value <- combined_data_with_total_value %>%
  mutate(log_population = log(population))
combined_data_with_total_value
```



#### * Perform a left join to add gdp, net_immigration, scholarship_ODA and total_unemployment_rate to combined_data based on 'year' and 'Academic_year' (remove column destination)
```{r}
combined_data1 <- combined_data %>%
  group_by(Academic_year, Country, study_destination) %>%
  summarize(total_students = sum(total_students, na.rm = TRUE), .groups = "drop")
  
# Perform a left join to add gdp, net_immigration and total_uemployment_rate to combined_data based on 'year' and 'Academic_year'
combined_data_with_total_value1 <- combined_data1%>%
  left_join(yearly_sum_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_net_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_unemployment_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_population_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(scholarship_ODA, by = c("Academic_year" = "Academic_year", "Country" = "Country"))
  
```


```{r}
# Replace missing value in scholarship become 0 
combined_data_with_total_value1$scholarship_ODA_volume[is.na(combined_data_with_total_value1$scholarship_ODA_volume)] <- 0
```

```{r}
# Create log(population)
combined_data_with_total_value1 <- combined_data_with_total_value1 %>%
  mutate(log_population = log(population))
combined_data_with_total_value1

```


# II/ Discussion & Interpreation

## Checking residuals & Adjustment
```{r}
combined_data_with_total_value2 <- combined_data_with_total_value1 %>%
  filter(scholarship_ODA_volume != 0) %>%   # exclude rows with 0 scholarships
  arrange(study_destination, Academic_year) %>%
  group_by(study_destination) %>%
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()



# Create binary columns for Country
country_binary <- model.matrix(~ Country - 1, data = combined_data_with_total_value2)
# Create binary columns for Study destination
destination_binary <- model.matrix(~ study_destination - 1, data = combined_data_with_total_value2)

# Combine with original data (excluding original categorical columns)
selected_data_binary <- cbind(
  combined_data_with_total_value2 %>% select(-Country, -study_destination, -total_students),
  country_binary,
  destination_binary
)
# Regression model of all data set
lm_preliminary_result <- lm(pct_change_students ~., selected_data_binary)
summary(lm_preliminary_result)
```




### Check the normality of the regression model
```{r}
# Residual plot
plot(lm_preliminary_result, which = 1)
```

### Identify the residuals' location
```{r}
# Compute residuals
res <- residuals(lm_preliminary_result)

# For find all residuals above a certain threshold
threshold <- 50000  # Base on the residual plot
problematic_rows <- which(abs(res) > threshold)

# View the actual data points causing the problem
lm_preliminary_result$model[problematic_rows, ]
```

Base on the actual data points causing the problem, these data are coming from Pakistan. Therefore, we will remove it for accuracy, which means there will be 30 Asian countries afterward.

### Re-check residual
```{r}
# Remove Pakistan
combined_data_with_total_value3 <- combined_data_with_total_value1 %>%
  filter(!Country %in% c("Pakistan"))

combined_data_with_total_value4 <- combined_data_with_total_value3 %>%
    filter(scholarship_ODA_volume != 0) %>%   # exclude rows with 0 scholarships
  arrange(study_destination, Academic_year) %>%
  group_by(study_destination) %>%
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()

# Create binary columns for Country
country_binary <- model.matrix(~ Country - 1, data = combined_data_with_total_value4)
# Create binary columns for Study destination
destination_binary <- model.matrix(~ study_destination - 1, data = combined_data_with_total_value4)

# Combine with original data (excluding original categorical columns)
selected_data_binary <- cbind(
  combined_data_with_total_value4 %>% select(-Country, -study_destination, -total_students),
  country_binary,
  destination_binary
)
# Regression model of all data set
lm_preliminary_result <- lm(pct_change_students ~., selected_data_binary)
summary(lm_preliminary_result)
```


```{r}
# Residual plot

plot(lm_preliminary_result, which = 1)

```

Based on the second residual vs. fitted plot, the residuals still become spread out gradually after 50000. Therefore, running a second residual vs. fitted plot for one more time is essential

### Identify the residuals' location
```{r}
# Compute residuals
res <- residuals(lm_preliminary_result)

threshold <- 50000

# Find rows with residuals outside the range
problematic_rows <- which(abs(res) > threshold)

# View the actual data points causing the problem
lm_preliminary_result$model[problematic_rows, ]
```

We can see that Philippines is also contributing to the heteroskedasticity of the plot, so we will remove remove this country from data set.
 
### Re-check residual one last time
```{r}
# Remove Pakistan & Philippines
combined_data_with_total_value5<- combined_data_with_total_value3%>%
  filter(!Country %in% c("Pakistan", "Philippines"))

combined_data_with_total_value6<- combined_data_with_total_value5%>%
    filter(scholarship_ODA_volume != 0) %>%   # exclude rows with 0 scholarships
  arrange(study_destination, Academic_year) %>%
  group_by(study_destination) %>%
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()

# Create binary columns for Country
country_binary <- model.matrix(~ Country - 1, data = combined_data_with_total_value6)
# Create binary columns for Study destination
destination_binary <- model.matrix(~ study_destination - 1, data = combined_data_with_total_value6)

# Combine with original data (excluding original categorical columns)
selected_data_binary <- cbind(
  combined_data_with_total_value6 %>% select(-Country, -study_destination, -total_students),
  country_binary,
  destination_binary
)
# Regression model of all data set
lm_preliminary_result <- lm(pct_change_students ~., selected_data_binary)
summary(lm_preliminary_result)
```
 
```{r}
# Residual plot
plot(
  lm_preliminary_result,
  which = 1,
  main = "Linear regression of stuents change model",
  sub = "All Other Predictors"
)
```
 
 

 
```{r}

#  Aggregate total students by year and study destination ( calculate percentage change over years for each countries)
aggregated_data <- combined_data_with_total_value5 %>%
  group_by(Academic_year, study_destination) %>%
  summarise(total_students = sum(total_students, na.rm = TRUE)) %>%
  arrange(study_destination, Academic_year) %>%
  group_by(study_destination) %>%
  # Compute year-over-year % change
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()

# Plot % change over time
ggplot(aggregated_data, aes(x = Academic_year, y = pct_change_students, 
                            color = study_destination, group = study_destination)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
   geom_vline(xintercept = 2020, linetype = "dashed", color = "black", size = 0.8) +
  annotate("text", x = 2020.2, y = max(aggregated_data$pct_change_students, na.rm = TRUE),
           label = "COVID-19 Travel restrictions ", hjust = 0, vjust = 1, size = 2.7, color = "black") +
  labs(
    title = "Figure 1: Percentage change in Total Students",
    subtitle = "from 29 Asian countries",
    x = "Year",
    y = "Change in Total Students (%)",
    color = "Study Destination"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(size = 12,  hjust = 0.5),
        plot.subtitle = element_text(size = 12, hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

 
 
 
## Line plot of students studying abroad in United States from 2016 to 2023
```{r}
df_us_inflows <- combined_data_with_total_value6 %>%
  # Filter for only the United States as the study destination
  filter(study_destination == "United States") %>%
    group_by(Academic_year) %>%
    summarise(Total_Students_US = sum(total_students, na.rm = TRUE)) %>%
  ungroup()
```

 
```{r}
us_plot <- ggplot(df_us_inflows, aes(x = Academic_year, y = Total_Students_US)) +
  geom_line(color = "black", linewidth = 1.2) +    labs(
    title = "United States",
    x = "Academic Year",
    y = "Total Number of Students"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(size = 10),      
    axis.title.x = element_text(size = 10),  
    axis.title.y = element_text(size = 10),    
    axis.text.x = element_text(size = 8),     
    axis.text.y = element_text(size = 8)       
  )

us_plot
```

 

 
 
 
 
```{r}
# Top 2 in dataset has the highest number of Asian students studying
combined_data_with_total_value7 <- combined_data_with_total_value %>%
  filter(!Country %in% c("Pakistan", "Philippines"))

df_germany_inflows <- combined_data_with_total_value7 %>%
  # Filter for only the Germany as the study destination
  filter(destination== "Germany") %>%
    group_by(Academic_year) %>%
    summarise(Total_Students_Germany = sum(total_students, na.rm = TRUE)) %>%
  ungroup()
```




```{r}
germany_plot <- ggplot(df_germany_inflows, aes(x = Academic_year, y = Total_Students_Germany)) +
  geom_line(color = "black", linewidth = 1.2) +    labs(
    title = "Germany",
    x = "Academic Year",
    y = "Total Number of Students"
  ) +
  theme_minimal()+
  theme(
    plot.title = element_text(size = 10),      
    axis.title.x = element_text(size = 10),  
    axis.title.y = element_text(size = 10),    
    axis.text.x = element_text(size = 8),     
    axis.text.y = element_text(size = 8)       
  )

germany_plot <- germany_plot +
  scale_y_continuous(labels = label_comma())

```

 
 
```{r}
# Top 3 in dataset has the highest number of Asian students studying
df_france_inflows <- combined_data_with_total_value7 %>%
  # Filter for only the Germany as the study destination
  filter(destination== "France") %>%
    group_by(Academic_year) %>%
    summarise(Total_Students_France = sum(total_students, na.rm = TRUE)) %>%
  ungroup()
```



 
```{r}
# Top 3 in dataset has the highest number of Asian students studying
france_plot <- ggplot(df_france_inflows, aes(x = Academic_year, y = Total_Students_France)) +
  geom_line(color = "black", linewidth = 1.2) +    labs(
    title = "France",
    x = "Academic Year",
    y = "Total Number of Students"
  ) +
  theme_minimal()+
  theme(
    plot.title = element_text(size = 10),      
    axis.title.x = element_text(size = 10),  
    axis.title.y = element_text(size = 10),    
    axis.text.x = element_text(size = 8),     
    axis.text.y = element_text(size = 8)       
  )


```





```{r}
# Find the top 5 destination
# Turkiye has naming error, so we will fix by UTF8
combined_data_with_total_value7$destination[
  combined_data_with_total_value7$destination == "T\xfcrkiye"
] <- "Türkiye"


top5_dest <- combined_data_with_total_value7 %>%
  group_by(destination) %>%
  summarise(total_students_sum = sum(total_students, na.rm = TRUE)) %>%
  arrange(desc(total_students_sum)) %>%
  slice_head(n = 5) %>%
  pull(destination)

filtered_data <- combined_data_with_total_value7 %>%
  filter(destination %in% top5_dest)

plot_data <- filtered_data %>%
  group_by(Academic_year) %>%
  summarise(total_students = sum(total_students, na.rm = TRUE), .groups = "drop")



top5_plot <- ggplot(plot_data, 
       aes(x = Academic_year, 
           y = total_students, )) +
  geom_line(size = 1.2) +
  labs(
    title = "Top 5 Destinations",
    x = "Academic Year",
    y = "Total Students"
  ) +
  theme_minimal()+
  theme(
    plot.title = element_text(size = 10),     
    axis.title.x = element_text(size = 10),  
    axis.title.y = element_text(size = 10),    
    axis.text.x = element_text(size = 8),     
    axis.text.y = element_text(size = 8)       
  )

top5_plot

```


#### Show all plots in 1 place
```{r}
combined_plot <- (us_plot | germany_plot) / (france_plot | top5_plot) +
  plot_annotation(title = "Figure 2: Comparative Visualization of Top 1, 2, 3 &  Top 5 Study Destinations of Asian students",
                  theme = theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5) # adjust size here
    )
  )
combined_plot
```

# Decide DiD (Difference-in-Differences) type

### DiD before vs after 2020 (Europe as treated group)\

Because we focus on comparing only two study destinations (Europe vs United States). Therefore, a simple pairwise DiD is not suitable, and using a fixed-effects DiD with country and year controls will provide a cleaner and more robust estimate of the effect while accounting for overall differences across countries and time trends.

```{r}

# Combine with original data (excluding original categorical columns)
selected_data_binary4 <- cbind(
  combined_data_with_total_value6 %>% select(-study_destination, -total_students),
  destination_binary
)
```



```{r}
# Create dummy variable post2020 for selected_data_binary4
selected_data_binary5<- selected_data_binary4 %>%
  mutate(
    post2020 = ifelse(Academic_year >= 2020, 1, 0)
  )
# Fixed effect of studying in Europe after 2020 on pct_change_students, controlling for other country/year-level covariates
did_fe <- feols(
  pct_change_students ~ post2020 * study_destinationEurope +
    gdp + net_immigration + population + unemployment_rate +
    scholarship_ODA_volume + log_population |
    Country + Academic_year,
  data = selected_data_binary5
)

etable(did_fe)
```

```{r}
summary(did_fe, vcov = "HC1")  # robust standard errors

```
 

 
 
```{r}

# Fit the model
lm_model <- lm(pct_change_students ~ . - population, data = selected_data_binary5)

# Robust variance-covariance
robust_vcov <- vcovHC(lm_model, type = "HC3")

# Robust coeftest
robust_summary <- coeftest(lm_model, vcov = robust_vcov)

# Convert to a tidy data frame safely
ci_df <- data.frame(
  term = rownames(robust_summary),
  Estimate = robust_summary[, 1],
  Std_Error = robust_summary[, 2],
  t_value = robust_summary[, 3],
  P_value = robust_summary[, 4]
) %>%
  filter(str_detect(term, "^Country")) %>%  # keep only country dummies
  mutate(
    Country = str_remove(term, "^Country"),
    Lower_CI = Estimate - 1.96 * Std_Error,
    Upper_CI = Estimate + 1.96 * Std_Error
  ) %>%
  arrange(Estimate) %>%
  mutate(Country = factor(Country, levels = Country))

# Forest plot
forest_plot <- ggplot(ci_df, aes(x = Estimate, y = Country)) +
  geom_errorbarh(aes(xmin = Lower_CI, xmax = Upper_CI), height = 0.2, linewidth = 1, color = "grey") +
  geom_point(size = 3, color = "black") +
  geom_point(data = filter(ci_df, P_value < 0.05), size = 3, color = "red") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
  labs(
    title = "How Each Country's Student Growth Compares to Maldives (95% CI)",
    subtitle = paste("Reference Country:", ci_df$Country[1]),
    x = "Effect on Pct Change Students",
    y = NULL
  ) +
  theme_minimal() +
  theme(plot.title.position = "plot")

print(forest_plot)


```

```{r}
# 2. Create an event_time variable centered around the treatment year (2020)
# This creates a variable where: ... -2 (2018), -1 (2019), 0 (2020), 1 (2021), 2 (2022) ...
selected_data_binary5 <- selected_data_binary5 %>%
  mutate(event_time = Academic_year - 2020)

# 3. Set the reference period (pre-treatment) to 2019 (event_time = -1)
selected_data_binary5$event_time_factor <- factor(selected_data_binary5$event_time)
selected_data_binary5$event_time_factor <- relevel(selected_data_binary5$event_time_factor, ref = "-1")

# 4. Run the Event Study DiD model
event_study <- feols(
  pct_change_students ~ i(event_time_factor, study_destinationEurope, ref = "-1") +
    gdp + net_immigration + population + unemployment_rate +
    scholarship_ODA_volume + log_population |
    Country + Academic_year, # Include all fixed effects
  data = selected_data_binary5,
  cluster = ~Country # Use clustered standard errors for robust inference
)

# Plot Event Study
iplot(
  event_study,
  ci_level = 0.95,                 
  xlab = "Years Relative to 2020",
  ylab = "Effect on % Change in Students",
  main = "Event Study: Effect of Study Destination Europe on Student Flows",
  ref.line = 0,
  col = "black",
  lwd = 2
)

# Add subtitle below the title
mtext(
  "Using 2019 as reference year (0 in x-axis), clustered by 23 Countries receiving ODA scholarship",
  side = 3,      # top
  line = 0.5,    # distance from main title
  cex = 0.7      # size of subtitle
)

```



